On-the-fly Algorithms for GKAT Equivalences \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-01-17 main.tex
change implementation description to match algorithm

Notice that during bisimulation~(\Cref{alg:symb-bisim}) for some \(s \in S\) and \(u \in U\), if there is \((b,s',p) \in \hat{\delta}_S(s)\) where \(b\) is a semantically false boolean expression, then implications of form \((b \land \cdot) \not{\equiv} 0 \Rightarrow \cdot\) are trivially satisfied. In other words, \textit{blocked} transitions in \(S\) do not contribute to the result of bisimulation. The same observation holds true symmetrically for \(U\). So blocked transitions of a coalgebra can be safely pruned without impacting the result of bisimulation.

>>>>

Notice that during bisimulation~(\Cref{alg:symb-bisim}) for some \(s \in S\) and \(u \in U\), if there is \(s \transvia{b ∣ p} s'\), i.e. \((b,s',p) \in \hat{\delta}_S(s)\), where \(b\) is a semantically false boolean expression, then implications with premises of the form \((b \land \cdot) \not{\equiv} 0\) are trivially satisfied. In other words, \textit{blocked} transitions in \(S\) do not contribute to the result of bisimulation. The same observation holds true symmetrically for \(U\). So blocked transitions of a coalgebra can be safely pruned without impacting the result of bisimulation.
